Monte Carlo tree search compared to A\(^*\) in airspace configuration decision problem

### 2018-05-15 article/article.tex
(+) More tests and further work

In most cases the cost of a configuration is based on the workload. Each
approach seems to give their own representation of the workload. For instance,
~\cite{bedouet2016towards} determined workload density proportionally to the time
spent by aircraft in each sector. A simpler version~\cite{sergeeva2017dynamic}
only uses the number of aircraft. On the other hand, more complex methods,
involving many more inputs are also available. For
instance,~\cite{gianazza2010forecasting} used several indicators, such as sector
volume, or vertical incoming flows in the next 15 and 60 minutes. Those
indicators ease the training of a neural network forecasting the workload.

@@

Considering paragraph~\ref{ssec:theoretical_performances}, the MCTS should
eventually converge to the optimal value, and this result reveals a flaw in the
implementation of the algorithm.
\begin{figure}
  \begin{tikzpicture}
    \begin{axis}
      [line width=0.05, mark size=0.1, xlabel=time(s), ylabel=cost]
      \addplot+ table {data/longterm.data};
      \addplot+[dashed, domain=0:10] {1268};
    \end{axis}
  \end{tikzpicture}
  \caption{The continuous line shows the total cost of a path computed by the
    MCTS algorithm. The x-axis shows the time allowed to the algorithm. The
    dashed curve is 15\% of the optimal cost found with the \(A^*\)
  algorithm.}\label{fig:longterm}
\end{figure}

\subsection{Speed}
To measure

\subsection{Further work}

>>>>

In most cases the cost of a configuration is based on the workload. Each
approach seems to give their own representation of the workload. For instance,
\cite{bedouet2016towards} determined workload density proportionally to the time
spent by aircraft in each sector. A simpler version~\cite{sergeeva2017dynamic}
only uses the number of aircraft. On the other hand, more complex methods,
involving many more inputs are also available. For
instance,~\cite{gianazza2010forecasting} used several indicators, such as sector
volume, or vertical incoming flows in the next 15 and 60 minutes. Those
indicators ease the training of a neural network forecasting the workload.

@@

Considering paragraph~\ref{ssec:theoretical_performances}, the MCTS should
eventually converge to the optimal value. This result reveals a flaw in the
implementation.
\begin{figure}
  \begin{tikzpicture}
    \begin{axis}
      [line width=0.05, mark size=0.1, xlabel=time(s), ylabel=cost]
      \addplot+ table {data/longterm.data};
      \addplot+[dashed, domain=0:10] {1268};
    \end{axis}
  \end{tikzpicture}
  \caption{The continuous line shows the total cost of a path computed by the
    MCTS algorithm. The x-axis shows the time allowed to the algorithm. The
    dashed curve is 15\% of the optimal cost found with the \(A^*\)
  algorithm.}\label{fig:longterm}
\end{figure}

\subsection{Converging speed}
Since the MCTS converges to a solution, one expects to know the time required to
be close enough to the optimal solution. To have an idea of this lapse, several
MCTS are run with different computing time. This results in a graph mapping the
time allowed to compute each step of the MCTS to the cost of the final path. To
get rid of the undesired varations due to the stochastic nature of the
algorithm, the latter process is run several times; which allows one to compute
the mean over all computed costs.

The resulting graphs are shown in figure~\ref{fig:longterm} in which it can be
seen that the algorithm reaches its best cost when it runs for 2 seconds per
step.

\begin{figure}
  \begin{tikzpicture}
    \begin{axis}
      [line width=0.05, mark size=0.1, xlabel=depth, ylabel=cost]
      \addplot+[dashed, domain=100:800] {18};
    \end{axis}
  \end{tikzpicture}
  \caption{The nice graph}\label{fig:timedepth}
\end{figure}

The converging speed may also depend on the depth of the tree searched through.
The figure~\ref{fig:timedepth} shows

\subsection{Further work}
Since all the tests has been run using Paris West area, the influence of the
complexity of the airspace has not been assessed. It would be thus relevant to
carry further tests on bigger areas. In~\cite{ferrari2017}, the time needed to
compute the cost with A\(^*\) depends heavily on the traffic itself. Therefore
the use, in this paper, of randomly generated scenarii of traffic may not be
suitable in the context of ATM. One can even use a more realistic workload model
such as a neural network as mentioned in~\cite{gianazza2010forecasting}.
